Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-06 writeups/proposal/proposal.tex
foo
Former-commit-id: 6f33a13acf79593b4d3fbd36583210f58a52dc85 [formerly 3af3fba524bb1edaacd3fcfb4e12fd972b2cabb1]
Former-commit-id: a8fa7817fe0fb7a3741fbdde67e5d9f91bd038d5

\textcite{Stanley2013} also modeled a user's chosen tags for a post on the StackOverflow site.
The model was based on ACT-R's declarative memory retrieval theory, which at the core is also a Bayesian co-occurrence model.
However several modifications to the model were made from the standard Bayesian ACT-R declarative memory theory, so it was more sophisticated than the standard ACT-R model and the model used by \textcite{Kuo2011}.
\citeauthor{Stanley2013} used a data-driven entropy weighting measure to attenuate low-predictor words and increase the weighting of high-predictor words in the body and title of a post.
An offset term was also included which leveled the model's overall prediction for each post and enabled the use of a logistic regression statistical technique to calibrate the model's parameters.
A separate model component was used for the words in the body and title of the post, and it was unclear if \citeauthor{Kuo2011} used the words in the body of the post for his models.

@@

%The SNIF-ACT model uses strength of association to measure the relationship between the words in a search query and the words contained in each query result.
%A higher $S_{ji}$ between a query and a result means that the result is a better fit for the query, and that the user is more likely to click on that link.
%The links that user chose in experimental testing were largely predictive of the strength of association measure.

%TODO: This paragraph doesn't fit well after the previous one, and in the scaling section
%The predictive power of the SNIF-ACT model went above and beyond what would be predicted by simply assuming that the user always clicks on the first link in the search results page.

% ref: http://tex.stackexchange.com/questions/53513/hyperref-token-not-allowed
\subsubsection{\texorpdfstring{\textcite{Stanley2013}}{Stanley2013}'s ACT-R DM Model for StackOverflow}

\textcite{Stanley2013} modified the standard ACT-R model in Table \ref{tabACT-RModel} in order to more accurately predict tag use on StackOverflow.
A formal description of the modified ACT-R Bayesian model is included in Table \ref{tabModACTRModel}.

@@

>>>>

@@

@@

% ref: http://tex.stackexchange.com/questions/53513/hyperref-token-not-allowed
\paragraph{\texorpdfstring{\textcite{Stanley2013}}{Stanley2013}'s ACT-R DM Model for StackOverflow}

\textcite{Stanley2013} also modeled a user's chosen tags for a post on the StackOverflow site.
They modified the standard ACT-R model in Table \ref{tabACT-RModel} in order to more accurately predict tag use on StackOverflow.
A formal description of the modified ACT-R Bayesian model is included in Table \ref{tabModACTRModel}.

\paragraph{Comparison Between \citeauthor{Kuo2011}'s and \citeauthor{Stanley2013}'s Models}

\textcite{Stanley2013}'s model was based on ACT-R's declarative memory retrieval theory, which at the core is also a Bayesian co-occurrence model.
However several modifications to the model were made from the standard Bayesian ACT-R declarative memory theory, so it was more sophisticated than the standard ACT-R model and the model used by \textcite{Kuo2011}.
\citeauthor{Stanley2013} used a data-driven entropy weighting measure to attenuate low-predictor words and increase the weighting of high-predictor words in the body and title of a post.
An offset term was also included which leveled the model's overall prediction for each post and enabled the use of a logistic regression statistical technique to calibrate the model's parameters.
A separate model component was used for the words in the body and title of the post, and it was unclear if \citeauthor{Kuo2011} used the words in the body of the post for his models.
